Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-05-14 figures.Rmd
fix font in supplement

**Figure S1.** Plotted are the individual logistic regression curves of individual variables tested for their discriminatory power between UM and CM. On the y-axis, 1 represents CM while 0 represents UM. A steeper curve indicates higher discriminatory power
### Supplementary figure 2: Spearman correlations of NIRS variables 
```{r fig_s2, fig.show = "hold", out.width = "50%", fig.height = 12, fig.width = 15}

>>>>

**Figure S1.** Plotted are the individual logistic regression curves of individual variables tested for their discriminatory power between UM and CM. On the y-axis, 1 represents CM while 0 represents UM. A steeper curve indicates higher discriminatory power

### Supplementary figure 2: Spearman correlations of NIRS variables 
```{r fig_s2, fig.show = "hold", out.width = "50%", fig.height = 12, fig.width = 15}
